---
title: "GOA Plan Team Report"
author: "Gulf of Alaska Plan Team"
date: "11/27/2021"
output:
  html_document:
    theme: united
    highlight: tango 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, message = F, warning = F, error = F)
library(flextable)
library(tidyverse) 
```

```{r data}
year = 2021
df <- read_csv("sheet.csv",na=c("","NA","n/a"))
```

```{r functions}


sum_tbl <- function(spp, df){
  df %>%  
  filter(Species==spp) %>% 
  select(2:10) %>%  
    flextable::flextable()
}

app_tbl <- function(spp, df){
  df %>%  
  filter(Species==spp) %>% 
  select(c(2,8,10))  %>%  
    flextable::flextable()
}
```

# Totals


```{r summary}
df %>%  
  filter(Species!="TOTAL",Area=="Total") %>% 
  select(c(1,3:5,7:10)) %>% 
  bind_rows(summarise(., across(where(is.numeric), sum),
      across(where(is.character), ~"Total")))  %>%  
    flextable::flextable() %>% 
  flextable::autofit()
```

```{r, child=c('pollock.Rmd', 'pcod.Rmd')}
```




## `r  spp<-"Sablefish";spp`
```{r spp3}
sum_tbl(spp, df) 
```

### Changes from the previous assessment

### Spawning biomass and stock trends

### Tier determination, ABCs and OFLs

### Status determination

### Area apportionment

```{r spp3aa}
app_tbl(spp, df) 
```


## `r  spp<-"Shallow-water Flatfish";spp`
```{r spp4}
sum_tbl(spp, df) 
```


### Changes from the previous assessment

### Spawning biomass and stock trends

### Tier determination, ABCs and OFLs

### Status determination

### Area apportionment 

```{r spp4aa)}
app_tbl(spp, df) 
```

## `r  spp<-"Deep-water Flatfish";spp`
```{r spp5}
sum_tbl(spp, df) 
```

### Changes from the previous assessment

### Spawning biomass and stock trends

### Tier determination, ABCs and OFLs

### Status determination

### Area apportionment

```{r spp5aa)}
app_tbl(spp, df) 
```

## `r  spp<-"Rex Sole";spp`
```{r spp6}
sum_tbl(spp, df) 
```

### Changes from the previous assessment

### Spawning biomass and stock trends

### Tier determination, ABCs and OFLs

### Status determination

### Area apportionment
```{r spp6aa)}
app_tbl(spp, df) 
```

## `r  spp<-"Arrowtooth Flounder";spp`
```{r spp7}
sum_tbl(spp, df) 
```


### Changes from the previous assessment

### Spawning biomass and stock trends

### Tier determination, ABCs and OFLs

### Status determination

### Area apportionment
```{r spp7aa)}
app_tbl(spp, df) 
```

## `r  spp<-"Flathead Sole";spp`
```{r spp8}
sum_tbl(spp, df) 
```

### Changes from the previous assessment

### Spawning biomass and stock trends

### Tier determination, ABCs and OFLs

### Status determination

### Area apportionment
```{r spp8aa)}
app_tbl(spp, df) 
```

## `r  spp<-"Pacific ocean perch";spp`
```{r spp9}
sum_tbl(spp, df) 
```

### Changes from the previous assessment

### Spawning biomass and stock trends

### Tier determination, ABCs and OFLs

### Status determination

### Area apportionment
```{r spp9aa)}
app_tbl(spp, df) 
```

## `r  spp<-"Northern Rockfish";spp`
```{r spp10}
sum_tbl(spp, df) 
```
### Changes from the previous assessment

### Spawning biomass and stock trends

### Tier determination, ABCs and OFLs

### Status determination

### Area apportionment
```{r spp10aa)}
app_tbl(spp, df) 
```

## `r  spp<-"Shortraker Rockfish";spp`
```{r spp11}
sum_tbl(spp, df) 
```

## `r  spp<-"Dusky Rockfish";spp`
```{r spp12}
sum_tbl(spp, df) 
```

## `r  spp<-"Rougheye and Blackspotted Rockfish";spp`
```{r spp13}
sum_tbl(spp, df) 
```


## `r  spp<-"Demersal shelf rockfish";spp`
```{r spp14}
sum_tbl(spp, df) 
```

## `r  spp<-"Thornyhead Rockfish";spp`
```{r spp15}
sum_tbl(spp, df) 
```
